---
title: "State_timeseries"
author: "Shreyashi Mukhopadhyay"
date: "4/13/2022"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```


## Install packages

```{r}
library(wesanderson)
library(ggplot2)
library(ggpubr)
library(foreign)
library(tidyverse)
library(dplyr)
library(readr)
library(lubridate)
library(RColorBrewer)
library(ggcorrplot)
library(stringr)
library(stargazer)
library(ggfortify)
library(forecast)
library(xts)
library(zoo)
library(fpp2)
library(TTR)
library(geofacet)
library(plotly)
library(plyr)
library(reshape)
library(gridExtra)

theme_set(theme_classic())

```


## Data pre-processing


## Read the data

```{r}

state= read.csv('State_time_series.csv')

sprintf("The data set has %d rows and %d columns", nrow(state), ncol(state) )

```



## Convert the date column into date format

```{r}

state$Date<-as.Date(state$Date)

#state <- separate(state, "Date", c("Year", "Month", "Day"), sep = '-')

```


## Creating the column Year from the Date column

```{r}

state['Year'] = year(state$Date)

head(state)
```


## Counting Null Values
```{r}

print(sum(is.na(state)))

```


## Setting the NA values to 0

```{r}
#state[is.na(state)] <- 0

```

## Dropping NA Null Values

```{r}

#state<-na.omit(state)

```


## Recounting the number of Null values

```{r}

#print(sum(is.na(state)))

```


## View structure and columns of the data

```{r}

str(state)

names(state)

head(state)

```
## Sale Price and Count By State from 1996-2017

```{r}

Each_state_s<-ddply(state, 'RegionName', summarise, 
                    price=mean(Sale_Prices, na.rm=T))
                    

Each_state_s<-na.omit(melt(Each_state_s))

col<-c(rep("black",2), rep("gray50",45)) #for axis.text.x

ggplot(Each_state_s,aes(x=reorder(RegionName,-value),y=value, group=variable ))+
  geom_col(aes(fill=variable),position="dodge", width = 0.6)+
  labs(x="States", y=NULL, title = "Sale Prices for All Homes across States from 1996-2017")+
  coord_flip()+
  expand_limits(x=0, y=0)+
  theme(axis.text.y=element_text(color=col, size = 7, vjust=0),
        plot.title=element_text(vjust=3, size=15))

```

## Rental Price and Count By State from 1996-2017

```{r}

Each_state_s<-ddply(state, 'RegionName', summarise, 
                    price=mean(MedianRentalPrice_AllHomes, na.rm=T))
                    

Each_state_s<-na.omit(melt(Each_state_s))

col<-c(rep("black",2), rep("gray50",45)) #for axis.text.x

ggplot(Each_state_s,aes(x=reorder(RegionName,-value),y=value, group=variable, fill = "lightblue"))+
  geom_col(position="dodge", width = 0.70)+
  labs(x="States", y=NULL, title = "Rental Prices All Homes across States from 1996-2017")+
  coord_flip()+
  expand_limits(x=0, y=0)+
  theme(axis.text.y=element_text(color=col, size = 7, vjust=0),
        plot.title=element_text(vjust=3, size=15))
  

```
## Median Listing Price for Single Family Residence Across All States 

```{r}

plot1<-aggregate(MedianListingPrice_SingleFamilyResidence ~Year+RegionName, state, mean) 
plot1

ggplot(plot1)+
 geom_bar(mapping = aes(x = RegionName , y = MedianListingPrice_SingleFamilyResidence) , stat = "identity" , fill = 'orange') +
 theme(axis.text.x = element_text(angle=90))+
 ggtitle("Median Listing Price for Single Family Residence Across States for 1996-2017")

```
## Median Listing Price for Single Family Residence By Year for 1996-2017

```{r}

plot11<-aggregate(MedianListingPrice_SingleFamilyResidence  ~Year+RegionName, state, mean)

plot11

ggplot(plot11)+
 geom_bar(mapping = aes(x = Year , y = MedianListingPrice_SingleFamilyResidence ) , stat = "identity" , fill = 'lightblue') +
 theme(axis.text.x = element_text(angle=90))+
 ggtitle("Median Listing Price for Single Family Residence By Year for 1996-2017")

```


### Median Listing Price for Single family residence Chloropleth

```{r}

USA<-map_data("state")
USA$region<-gsub(" ","", USA$region)
Allstates <-data.frame( region = tolower(aggregate(MedianListingPrice_SingleFamilyResidence ~ RegionName, state, mean)[,1]), 
                        Price = aggregate(MedianListingPrice_SingleFamilyResidence ~ RegionName,state,mean)[,2])%>%
            mutate(Rank = dense_rank(desc(Price)))%>%
            merge(USA, by = 'region')

map1<-arrange(Allstates, order)%>%
    ggplot(aes(long, lat, group=group, fill=Price))+
    geom_polygon()+
    geom_path(alpha=0.2)+
    labs(x=NULL, y=NULL, title = "Median Listing Price for Single Family Homes in US")+
    coord_map("polyconic")+
    coord_fixed(1.3)+
    scale_fill_gradientn(colors= wes_palette("FantasticFox1"))+
    theme(legend.text=element_text(size=8),
          plot.title=element_text(size=15),
          panel.background=element_blank())
ggplotly(map1)

```


## The Growth of Median Listing Price for sigle family residence in US from 1996-2017

```{r}

Year_state<-aggregate(MedianListingPrice_SingleFamilyResidence ~Year+RegionName, state, mean)
pal<-rep(brewer.pal(15, "Spectral"),10)

ggplot(Year_state, aes(group = RegionName ))+
  geom_line(aes(x=Year,y=MedianListingPrice_SingleFamilyResidence,color=RegionName), alpha=0.5, show.legend=F)+
  scale_color_manual(values=pal)+
  labs(title="The Growth of Median Listing Price for Single Family Homes in US", x=NULL,
       subtitle="\t Increase in MedianListingPrice_SingleFamilyResidence from 1996 to 2017")+
  theme(panel.background=element_rect(fill = "white"),
          plot.title=element_text(vjust=3, size=15),
          panel.grid.major=element_line(color = "gray90"))


```




## Median Rental Prices for Single Family Home across States for 1996-2017

```{r}

plot2<-aggregate(MedianRentalPrice_SingleFamilyResidence ~Year+RegionName, state, mean)
plot2

ggplot(plot2)+
 geom_bar(mapping = aes(x = RegionName , y = MedianRentalPrice_SingleFamilyResidence  ) , stat = "identity" , fill = 'orange') +
 theme(axis.text.x = element_text(angle=90))+
 ggtitle("Median Rental Price for Single family Home by State for 1996-2017")


```
## Median Rental Price for All Homes across Years for 1996-2017

```{r}

plot12<-aggregate(MedianRentalPrice_SingleFamilyResidence ~Year+RegionName, state, mean)
plot12

ggplot(plot12)+
 geom_bar(mapping = aes(x = Year , y = MedianRentalPrice_SingleFamilyResidence  ) , stat = "identity" , fill = 'lightblue') +
 theme(axis.text.x = element_text(angle=90))+
 ggtitle("Median Rental Price for Single family Home by Year for 1996-2017")

```
### Median Rental Price for All Homes Chloropleth

```{r}

USA<-map_data("state")
USA$region<-gsub(" ","", USA$region)
Allstates <-data.frame( region = tolower(aggregate(MedianRentalPrice_SingleFamilyResidence ~ RegionName, state, mean)[,1]), 
                        Price = aggregate(MedianRentalPrice_SingleFamilyResidence  ~ RegionName,state,mean)[,2])%>%
            mutate(Rank = dense_rank(desc(Price)))%>%
            merge(USA, by = 'region')

map1<-arrange(Allstates, order)%>%
    ggplot(aes(long, lat, group=group, fill=Price))+
    geom_polygon()+
    geom_path(alpha=0.2)+
    labs(x=NULL, y=NULL, title = "Median Rental Price for Single family Home in US")+
    coord_map("polyconic")+
    coord_fixed(1.3)+
    scale_fill_gradientn(colors= wes_palette("Zissou1"))+
    theme(legend.text=element_text(size=8),
          plot.title=element_text(size=15),
          panel.background=element_blank())
ggplotly(map1)

```
## The Growth of Median Rental Price for All homes in US from 1996-2017

```{r}

Year_state<-aggregate(MedianRentalPrice_SingleFamilyResidence ~Year+RegionName, state, mean)
pal<-rep(brewer.pal(15, "Spectral"),10)

ggplot(Year_state, aes(group = RegionName ))+
  geom_line(aes(x=Year,y=MedianRentalPrice_SingleFamilyResidence,color=RegionName), alpha=0.5, show.legend=F)+
  scale_color_manual(values=pal)+
  labs(title="The Growth of Median Rental Price for Single family Home in US", x=NULL,
       subtitle="\t Increase in Median Rental Price from 1996 to 2017")+
  theme(panel.background=element_rect(fill = "white"),
          plot.title=element_text(vjust=3, size=15),
          panel.grid.major=element_line(color = "gray90"))


```

## Median Listing Price for All homes across States for 1996-2017

```{r}

plot3<-aggregate(ZHVI_SingleFamilyResidence ~Year+RegionName, state, mean)

plot3

ggplot(plot3)+
 geom_bar(mapping = aes(x = RegionName , y = ZHVI_SingleFamilyResidence ) , stat = "identity" , fill = 'orange') +
 theme(axis.text.x = element_text(angle=90))+
 ggtitle("ZHVI value for Single Family Homes across States for 1996-2017")

```

##ZHVI values Single Family Homes by Year for 1996-2017

```{r}

plot31<-aggregate(MedianListingPrice_AllHomes ~Year+RegionName, state, mean)

plot31

ggplot(plot31)+
 geom_bar(mapping = aes(x = Year , y = MedianListingPrice_AllHomes) , stat = "identity" , fill = 'lightblue') +
 theme(axis.text.x = element_text(angle=90))+
 ggtitle("ZHVI values for single family Homes by Year for 1996-2017")


```

### ZHVI values for Single Family Homes Chloropleth

```{r}

USA<-map_data("state")
USA$region<-gsub(" ","", USA$region)
Allstates <-data.frame( region = tolower(aggregate(MedianListingPrice_AllHomes ~ RegionName, state, mean)[,1]), 
                        Price = aggregate(MedianListingPrice_AllHomes ~ RegionName,state,mean)[,2])%>%
            mutate(Rank = dense_rank(desc(Price)))%>%
            merge(USA, by = 'region')

map1<-arrange(Allstates, order)%>%
    ggplot(aes(long, lat, group=group, fill=Price))+
    geom_polygon()+
    geom_path(alpha=0.2)+
    labs(x=NULL, y=NULL, title = "ZHVI values for single family Homes across states in US")+
    coord_map("polyconic")+
    coord_fixed(1.3)+
    scale_fill_gradientn(colors= wes_palette("FantasticFox1"))+
    theme(legend.text=element_text(size=8),
          plot.title=element_text(size=15),
          panel.background=element_blank())
ggplotly(map1)

```
## The Growth of Median Listing Price for All homes in US from 1996-2017

```{r}

Year_state<-aggregate(MedianListingPrice_AllHomes ~Year+RegionName, state, mean)
pal<-rep(brewer.pal(15, "Spectral"),10)

ggplot(Year_state, aes(group = RegionName ))+
  geom_line(aes(x=Year,y=MedianListingPrice_AllHomes,color=RegionName), alpha=0.5, show.legend=F)+
  scale_color_manual(values=pal)+
  labs(title="The Growth of ZHVI values for Single Family Homes across US", x=NULL,
       subtitle="\t Increase in Median Listing Price from 1996 to 2017")+
  theme(panel.background=element_rect(fill = "white"),
          plot.title=element_text(vjust=3, size=15),
          panel.grid.major=element_line(color = "gray90"))


```

## ZHVI for ALL Homes States for 1996-2017

```{r}

plot5<-aggregate(ZHVI_AllHomes ~ Year+RegionName, state, mean)
plot5

ggplot(plot5)+
 geom_bar(mapping = aes(x = RegionName , y = ZHVI_AllHomes) , stat = "identity" , fill = 'orange') +
 theme(axis.text.x = element_text(angle=90))+
 ggtitle("ZHVI for ALL Homes by State for 1996-2017")


```

## ZHVI for ALL Homes by Year for 1996-2017

```{r}

plot31<-aggregate(ZHVI_AllHomes ~Year+RegionName, state, mean)

plot31

ggplot(plot31)+
 geom_bar(mapping = aes(x = Year , y = ZHVI_AllHomes) , stat = "identity" , fill = 'lightblue') +
 theme(axis.text.x = element_text(angle=90))+
 ggtitle("ZHVI for ALL Homes by Year for 1996-2017")


```

## The Growth of ZHVI for ALL Homes in US from 1996-2017

```{r}

Year_state<-aggregate(ZHVI_AllHomes ~Year+RegionName, state, mean)
pal<-rep(brewer.pal(10, "Spectral"),5)

ggplot(Year_state, aes(group = RegionName ))+
  geom_line(aes(x=Year,y=ZHVI_AllHomes,color=RegionName), alpha=0.5, show.legend=F)+
  scale_color_manual(values=pal)+
  labs(title="The Growth in ZHVI for All Homes in US", x=NULL,
       subtitle="\t Increase in ZHVI_Allhomes from 1996 to 2017")+
  theme(panel.background=element_rect(fill = "white"),
          plot.title=element_text(vjust=3, size=15),
          panel.grid.major=element_line(color = "gray90"))


```

## Distribution of Plot Mean ZHVI for all Homes across all States


```{r}

USA<-map_data("state")
USA$region<-gsub(" ","", USA$region)
Allstates <-data.frame( region = tolower(aggregate(ZHVI_AllHomes ~ RegionName, state, mean)[,1]), 
                        Price = aggregate(ZHVI_AllHomes ~ RegionName,state,mean)[,2])%>%
            mutate(Rank = dense_rank(desc(Price)))%>%
            merge(USA, by = 'region')

map1<-arrange(Allstates, order)%>%
    ggplot(aes(long, lat, group=group, fill=Price))+
    geom_polygon()+
    geom_path(alpha=0.2)+
    labs(x=NULL, y=NULL, title = "Distribution of ZHVI values for all Homes across all States in US")+
    coord_map("polyconic")+
    coord_fixed(1.3)+
    scale_fill_gradientn(colors= wes_palette("Zissou1"))+
    theme(legend.text=element_text(size=8),
          plot.title=element_text(size=15),
          panel.background=element_blank())
ggplotly(map1)

```




## Mean ZHVI for 1 Bedroom House across all States


```{r}

library(ggplot2)
head(state)

plot111<-aggregate(ZHVI_1bedroom ~Year+RegionName, state, mean) 
plot111

ggplot(plot111)+
 geom_bar(mapping = aes(x = RegionName , y =ZHVI_1bedroom) , stat = "identity" , fill = 'pink') +
 theme(axis.text.x = element_text(angle=90))+
 ggtitle("ZHVI values for One Bedroom Homes Across States for 1996-2017")

```

## Plot Mean ZHVI for 2 Bedroom House across all States


```{r}

plot222<-aggregate(ZHVI_2bedroom ~Year+RegionName, state, mean) 
plot222

ggplot(plot222)+
 geom_bar(mapping = aes(x = RegionName , y =ZHVI_2bedroom) , stat = "identity" , fill = 'pink') +
 theme(axis.text.x = element_text(angle=90))+
 ggtitle("ZHVI values for Two Bedroom Homes Across States for 1996-2017")

```


## Mean ZHVI for 3 Bedroom House across all States


```{r}

plot333<-aggregate(ZHVI_3bedroom ~Year+RegionName, state, mean) 
plot333

ggplot(plot333)+
 geom_bar(mapping = aes(x = RegionName , y =ZHVI_3bedroom) , stat = "identity" , fill = 'pink') +
 theme(axis.text.x = element_text(angle=90))+
 ggtitle("ZHVI values for Three Bedroom Homes Across States for 1996-2017")



```

## Plot Mean ZHVI for 4 Bedroom House across all States


```{r}

plot444<-aggregate(ZHVI_4bedroom ~Year+RegionName, state, mean) 
plot444

ggplot(plot444)+
 geom_bar(mapping = aes(x = RegionName , y =ZHVI_4bedroom) , stat = "identity" , fill = 'pink') +
 theme(axis.text.x = element_text(angle=90))+
 ggtitle("ZHVI values for Four Bedroom Homes Across States for 1996-2017")

```


## Plot Mean ZHVI for 4 Bedroom House across all States


```{r}

plot555<-aggregate(ZHVI_5BedroomOrMore ~Year+RegionName, state, mean) 
plot555

ggplot(plot555)+
 geom_bar(mapping = aes(x = RegionName , y =ZHVI_5BedroomOrMore) , stat = "identity" , fill = 'pink') +
 theme(axis.text.x = element_text(angle=90))+
 ggtitle("ZHVI values for Five or more Bedroom Homes Across States for 1996-2017")


```

## Sale price for All Homes and All states


```{r}

gbp2<-wes_palette("GrandBudapest2")[2]

ggplot(state, aes(x=Sale_Prices))+
    geom_histogram(fill="pink", alpha=.9, binwidth=10000)+
    labs(x=NULL, y=NULL, title = "Median Sale Price for All Homes across All states")+
    scale_x_continuous(breaks= seq(0,600000, by=100000))+
    theme_minimal() + theme(plot.title=element_text(vjust=3, size=15) )



```
## Sale Prices Across states

```{r}


ggplot(state, aes(x=Sale_Prices))+
 geom_bar(mapping = aes(x = RegionName , y =Sale_Prices) , stat = "identity" , fill = 'pink') +
 theme(axis.text.x = element_text(angle=90))+
 ggtitle("Sale Prices Across States for 1996-2017")



```


### Sale price for All Homes across All States

```{r}

USA<-map_data("state")
USA$region<-gsub(" ","", USA$region)
Allstates <-data.frame( region = tolower(aggregate(Sale_Prices ~ RegionName, state, mean)[,1]), 
                        Price = aggregate(Sale_Prices ~RegionName,state,mean)[,2])%>%
            mutate(Rank = dense_rank(desc(Price)))%>%
            merge(USA, by = 'region')

ap<-arrange(Allstates, order)%>%
    ggplot(aes(long, lat, group=group, fill=Price))+
    geom_polygon()+
    geom_path(alpha=0.2)+
    labs(x=NULL, y=NULL, title = "Distribution of Sale Prices for AllHomes in US")+
    coord_map("polyconic")+
    coord_fixed(1.3)+
    scale_fill_gradientn(colors= wes_palette("Moonrise3"))+
    theme(legend.text=element_text(size=8),
          plot.title=element_text(size=15),
          panel.background=element_blank())
ggplotly(ap)

```

## Rental Prices for All homes and All States

```{r}

gbp2<-wes_palette("GrandBudapest2")[4]

ggplot(state, aes(x=MedianRentalPrice_AllHomes))+
    geom_histogram(fill=gbp2, alpha=.9, binwidth=100)+
    labs(x=NULL, y=NULL, title = "Median Rental Price for All Homes across All States")+
    scale_x_continuous(breaks= seq(0,4000, by=500))+
    theme( plot.title=element_text(vjust=3, size=15) ) + theme_minimal()




```



```{r}

USA<-map_data("state")
USA$region<-gsub(" ","", USA$region)
Allstates_r <-data.frame(region = tolower(aggregate(MedianRentalPrice_AllHomes ~ RegionName, state, mean)[,1]))%>%
              merge(USA, by = 'region')
meanr <-aggregate(MedianRentalPrice_AllHomes ~ RegionName, state, mean)
Allstates_r <-merge(Allstates_r, data.frame(price =meanr[,2], region =tolower(meanr[,1])),
                    all.x=TRUE)%>%
              mutate(Rank = dense_rank(-price))

ar<-arrange(Allstates_r, order)%>%
    ggplot(aes(long, lat, group=group, fill=price))+
    geom_polygon()+
    geom_path(alpha=0.2)+
    labs(x=NULL, y=NULL, title = "Distribution of the Average Median Rental Price for All Homes in US")+
    coord_map("FantasticFox1")+
    coord_fixed(1.3)+
    scale_fill_gradientn(colors= wes_palette("Moonrise3"))+
    theme(legend.text=element_text(size=8),
          plot.title=element_text(size=15),
          panel.background=element_blank())
ggplotly(ar)

```

## 

```{r}

gbp1<-wes_palette("GrandBudapest2")[1]

MSP <- aggregate(Sale_Prices ~Year, state, mean)

# MSP <-na.omit(ddply(data, 'Year', summarise, mean(Sale_Prices, na.rm=T)))

sl1 <-ggplot(MSP, aes(x=as.factor(Year), y=Sale_Prices))+
    geom_line(color=gbp1, aes(group=1), size=1.5)+
    geom_point(colour=gbp1, size = 3.5, alpha=0.5)+
    labs(title="The Growth of Sale Prices by year", x=NULL, y="Sale Price")+
    theme( plot.title=element_text(vjust=3, size=15) ) 



sl1
```

```{r}

MSP$rate = c(0, 100*diff(MSP$Sale_Prices)/MSP[-nrow(MSP),]$Sale_Prices)

sl2 <-ggplot(MSP, aes(x=as.factor(Year), y=rate))+
    geom_line(color= "gray50", aes(group=1), size=1)+
    #geom_point(colour=gbp1, size = 3.5, alpha=0.5)+
    labs(title="Change rate of Sale Price", x="Year", y="rate of change")+
    geom_hline(yintercept = 0, color = gbp1 )+
    theme(plot.title=element_text(size=15))+ theme_minimal()

sl2


```




## Growth of Sale price by State from 1996-2017

```{r}

library(wesanderson)
gbp1<-wes_palette("GrandBudapest2")[1]

MSP <- aggregate(Sale_Prices ~ RegionName, state, mean)


sl11 <-ggplot(MSP, aes(x=as.factor(RegionName), y=Sale_Prices))+
    geom_line(color=gbp1, aes(group=1), size=1.5)+
    geom_point(colour=gbp1, size = 3.5, alpha=0.5)+
    labs(title="The Growth of Sale Prices across years by State", x=NULL, y="Sale Price")+
    theme(axis.text.x = element_text(angle=90, hjust=1))


sl11


```
```{r}

library(wesanderson)
gbp2<-wes_palette("GrandBudapest2")[4]



MRP=na.omit(ddply(state,'Year',summarise,
                  Rental_price = mean(MedianRentalPrice_AllHomes , na.rm=T)))

rl1 <-ggplot(MRP, aes(x=as.factor(Year), y=Rental_price))+
    geom_line(color=gbp2, aes(group=1), size=1.5)+
    geom_point(colour=gbp2, size = 3.5, alpha=0.5)+
    labs(title="The Growth of Rental Prices by year", x=NULL, y="Rental_price")+
    theme( plot.title=element_text(vjust=3, size=20) ) 


rl1

```

```{r}

MRP$rate = c(0, 100*diff(MRP$Rental_price)/MRP[-nrow(MRP),]$Rental_price)
rl2 <-ggplot(MRP, aes(x=as.factor(Year), y=rate))+
    geom_line(color= "gray50", aes(group=1), size=1)+
    #geom_point(colour=gbp2, size = 3.5, alpha=0.5)+
    labs(title="Change rate of Rental Price", x="Year", y="rate of change")+
    geom_hline(yintercept = 0, color = gbp2 )+
    theme(plot.title=element_text(size=15)) + theme_minimal()



rl2
```
```{r}


library(wesanderson)
gbp1<-wes_palette("GrandBudapest2")[4]

MSP <- aggregate(MedianRentalPrice_AllHomes ~ RegionName, state, mean)


sl12 <-ggplot(MSP, aes(x=as.factor(RegionName), y=MedianRentalPrice_AllHomes))+
    geom_line(color=gbp1, aes(group=1), size=1.5)+
    geom_point(colour=gbp1, size = 3.5, alpha=0.5)+
    labs(title="The Growth of Rent Prices across years by State", x=NULL, y="Sale Price")+
    theme(axis.text.x = element_text(angle=90, hjust=1))


sl12



```

## Days on Zillow Analysis


```{r}


aggregate(Sale_Prices ~DaysOnZillow_AllHomes, state, mean)%>%
  ggplot(aes(x=DaysOnZillow_AllHomes, y=Sale_Prices))+
  geom_line(col=wes_palette("GrandBudapest2")[1])+
  labs(title="Days on Zillow effect House Sale prices Decreases", x="Days on Zillow", y="House Sale Price")+
    stat_smooth(method="loess", color="#0F327B", alpha=0.3)+
  theme_minimal()





```

## Days on Zillow effect on rent Prices

```{r}

aggregate(Sale_Prices ~DaysOnZillow_AllHomes, state, mean)%>%
  ggplot(aes(x=DaysOnZillow_AllHomes, y=Sale_Prices))+
  geom_line(col=wes_palette("GrandBudapest2")[4])+
  labs(title="Days on Zillow Increase effects House Rent Value Decrease", x="Days on Zillow", y="House Rental Price")+
   stat_smooth(method="loess", color="#0F327B", alpha=0.3)+
  theme_minimal()




```

## HOW DO THE HOME VALUES VARY BY TIER TYPE?


## DISTRIBUTION OF TOP TIER HOMES

```{r}
USA<-map_data("state")
USA$region<-gsub(" ","", USA$region)
Allstates <-data.frame( region = tolower(aggregate(ZHVI_TopTier ~ RegionName, state, mean)[,1]), 
                        Price = aggregate(ZHVI_TopTier ~RegionName,state,mean)[,2])%>%
            mutate(Rank = dense_rank(desc(Price)))%>%
            merge(USA, by = 'region')

ap<-arrange(Allstates, order)%>%
    ggplot(aes(long, lat, group=group, fill=Price))+
    geom_polygon()+
    geom_path(alpha=0.2)+
    labs(x=NULL, y=NULL, title = "ZHVI values for Top tier Homes in US")+
    coord_map("polyconic")+
    coord_fixed(1.3)+
    scale_fill_gradientn(colors= wes_palette("GrandBudapest2"))+
    theme(legend.text=element_text(size=8),
          plot.title=element_text(size=15),
          panel.background=element_blank())
ggplotly(ap)
```

## DISTRIBUTION OF MIDDLE TIER HOMES

```{r}
USA<-map_data("state")
USA$region<-gsub(" ","", USA$region)
Allstates <-data.frame( region = tolower(aggregate(ZHVI_MiddleTier   ~ RegionName, state, mean)[,1]), 
                        Price = aggregate(ZHVI_MiddleTier   ~RegionName,state,mean)[,2])%>%
            mutate(Rank = dense_rank(desc(Price)))%>%
            merge(USA, by = 'region')

ap<-arrange(Allstates, order)%>%
    ggplot(aes(long, lat, group=group, fill=Price))+
    geom_polygon()+
    geom_path(alpha=0.2)+
    labs(x=NULL, y=NULL, title = "ZHVI values for Middle Tier Homes in US")+
    coord_map("polyconic")+
    coord_fixed(1.3)+
    scale_fill_gradientn(colors= wes_palette("GrandBudapest2"))+
    theme(legend.text=element_text(size=8),
          plot.title=element_text(size=15),
          panel.background=element_blank())
ggplotly(ap)
```

## DISTRIBUTION OF BOTTOM TIER HOMES

```{r}
USA<-map_data("state")
USA$region<-gsub(" ","", USA$region)
Allstates <-data.frame( region = tolower(aggregate(ZHVI_BottomTier ~ RegionName, state, mean)[,1]), 
                        Price = aggregate(ZHVI_BottomTier~RegionName,state,mean)[,2])%>%
            mutate(Rank = dense_rank(desc(Price)))%>%
            merge(USA, by = 'region')

ap<-arrange(Allstates, order)%>%
    ggplot(aes(long, lat, group=group, fill=Price))+
    geom_polygon()+
    geom_path(alpha=0.2)+
    labs(x=NULL, y=NULL, title = "ZHVI values for Bottom Tier Homes in US")+
    coord_map("polyconic")+
    coord_fixed(1.3)+
    scale_fill_gradientn(colors= wes_palette("GrandBudapest2"))+
    theme(legend.text=element_text(size=8),
          plot.title=element_text(size=15),
          panel.background=element_blank())
ggplotly(ap)
```





### DISTRIBUTION OF HOUSE VALUES ACROSS TIERS




```{r}

tier = names(state)[grepl('Tier',names(state))]
 
total_distribution = state %>%
    select(ends_with('Tier')) %>% mutate(date=state$Date) %>%
  mutate(date=ymd(date)) %>%
  na.omit() %>%
  gather(type,value,1:3) %>%
  select(value)



options(scipen=999)
p = state %>%
  select(ends_with('Tier')) %>% mutate(date=state$Date) %>%
  mutate(date=ymd(date)) %>%
  na.omit() %>%
  gather(type,value,1:3) %>%
  ggplot(aes(x=value,fill=type))+geom_density(alpha=0.5, colour = "transparent")+facet_wrap(~type,nrow = 3)+
  theme(panel.background = element_rect(fill = '#ffffff'),
        axis.text.x = element_text(vjust=-1,angle=90),
        strip.background = element_blank(),
        legend.position = 'none',plot.title = element_text(hjust=0.5),plot.caption = element_text(hjust=-0.05,face='italic'))+labs(title='How do the house values vary by Tier type?',x='In USD',caption='The distribution in gray shows the overall distribution of the home values')+geom_density(data=total_distribution,aes(x=value),fill='gray',color='transparent',alpha=0.5)

p

 
ggsave(plot=p,filename='house_do_the_house_values_vary.png',width=17,height=10)


```
## Correlations

```{r}

library(corrplot)

subset1 = subset(state, select=c(DaysOnZillow_AllHomes, Sale_Prices, Sale_Counts, MedianListingPrice_AllHomes , MedianRentalPrice_AllHomes, ZHVI_1bedroom ,ZHVI_2bedroom ,ZHVI_3bedroom, ZHVI_4bedroom, ZHVI_5BedroomOrMore, ZHVI_AllHomes  ,ZHVI_BottomTier, ZHVI_MiddleTier, ZHVI_TopTier, ZHVI_CondoCoop, ZHVI_SingleFamilyResidence, ZHVIPerSqft_AllHomes, ZRI_AllHomes, Zri_SingleFamilyResidenceRental ))%>%na.omit()%>%cor()

subset1

corrplot1 = corrplot(subset1, hc.order = TRUE, outline.col = "white",  cl.pos = 'n', order = 'hclust', tl.cex=0.6, cl.ratio=0.2,
                   cl.cex=0.6, tl.col="black")

corrplot1


```
## Correlation Plot Number

```{r}

corrplot2 = corrplot(subset1, tl.cex=0.6, cl.ratio=0.2,
                   cl.cex=0.6, tl.col="black", order = "AOE", number.cex=0.75, , type = 'lower', diag = FALSE)

corrplot2


```

```{r}

corrplot3 = corrplot(subset1, tl.cex=0.6, cl.ratio=0.2,
                   cl.cex=0.6, tl.col="black", order = "AOE", number.cex=0.75, , type = 'upper', diag = FALSE)

corrplot3





```

```{r}



corrplot4 = corrplot(subset1, method = 'number', tl.cex=0.6, cl.ratio=0.2, cl.cex=0.6, tl.col="black", order = "AOE", number.cex=0.4, , type = 'upper', diag = FALSE)

corrplot4



```

```{r}

#tierwise = as.data.frame(state_max)
#str(tierwise)
#print(tierwise)


#ggplot(tierwise, aes(x = type, y =max_value, fill = type))  + geom_bar(stat="identity", color = origin)  + 

  #ggtitle("Distribution of House values by Tier Type")

```




## Distribution of Median Listing prices based on No. of Bedrooms

```{r}

listprice.df =  subset(state, select = c('Date', 'RegionName','MedianListingPrice_1Bedroom', 
'MedianListingPrice_2Bedroom', 'MedianListingPrice_3Bedroom', 
'MedianListingPrice_4Bedroom', 'MedianListingPrice_5BedroomOrMore', 'MedianListingPrice_CondoCoop'))

listprice.df$Date <- as.Date(listprice.df$Date, format = "%Y-%m-%d")

head(listprice.df)


ggplot(aes(x = MedianListingPrice_1Bedroom), data=listprice.df) +
geom_histogram(fill="LightPink", colour = "lightgreen", bins = 40) +
labs(x='One Bedroom', y='Count')

ggplot(aes(x=MedianListingPrice_2Bedroom), data=listprice.df) +
geom_histogram(fill="LightPink", colour = "lightgreen", bins = 40) +
labs(x='Two Bedroom', y='Count')

ggplot(aes(x=MedianListingPrice_3Bedroom), data=listprice.df) +
geom_histogram(fill="LightPink", colour = "lightgreen", bins = 40) +
labs(x='Three Bedroom', y='Count')

ggplot(aes(x=MedianListingPrice_4Bedroom), data=listprice.df) +
geom_histogram(fill="LightPink", colour = "lightgreen", bins = 40) +
labs(x='Four Bedroom', y='Count')

ggplot(aes(x= MedianListingPrice_5BedroomOrMore), data=listprice.df) +
geom_histogram(fill="LightPink", colour = "lightgreen", bins = 40) +
labs(x='Five Bedroom or More', y='Count')

ggplot(aes(x= MedianListingPrice_CondoCoop), data=listprice.df) +
geom_histogram(fill="LightPink", colour = "lightgreen",bins = 40) +
labs(x='Studio', y='Count')


```
## Median Rental Price per Sq feet 

```{r}

rental.df <- subset(state, select = c('Date', 'RegionName','MedianRentalPricePerSqft_1Bedroom', 
'MedianRentalPricePerSqft_2Bedroom', 'MedianRentalPricePerSqft_3Bedroom', 
'MedianRentalPricePerSqft_4Bedroom', 'MedianRentalPricePerSqft_5BedroomOrMore', 'MedianRentalPricePerSqft_Studio'))


## Distribution of Median Rental Price per sq feet based on No. of Bedrooms


ggplot(aes(x=MedianRentalPricePerSqft_1Bedroom), data=rental.df) +
geom_histogram(fill= "LightBlue", colour= "lightgreen", bins = 30) +
labs(x='One Bedroom', y='Count')

ggplot(aes(x=MedianRentalPricePerSqft_2Bedroom), data=rental.df) +
geom_histogram(fill="LightBlue", colour = "lightgreen",bins = 30) +
labs(x='Two Bedroom', y='Count')

ggplot(aes(x=MedianRentalPricePerSqft_3Bedroom), data=rental.df) +
geom_histogram(fill="LightBlue", colour = "lightgreen",bins = 30) +
labs(x='Three Bedroom', y='Count')


ggplot(aes(x=MedianRentalPricePerSqft_4Bedroom), data=rental.df) +
geom_histogram(fill="LightBlue", colour = "lightgreen",bins = 30) +
labs(x='Four Bedroom', y='Count')


ggplot(aes(x=MedianRentalPricePerSqft_5BedroomOrMore), data=rental.df) +
geom_histogram(fill="LightBlue", colour = "lightgreen",bins = 30) +
labs(x='Five Bedroom or More', y='Count')


ggplot(aes(x=MedianRentalPricePerSqft_Studio), data=rental.df) +
geom_histogram(fill="LightBlue", colour = "lightgreen",bins = 30) +
labs(x='Studio', y='Count')


```

```{r}





```

